Supporting Information Appendix:\\ Black-swan events in animal populations

### 2017-02-21 text/supp.tex
Tweak formatting in supplement
Fix newer Stan syntax

\begin{verbatim}
real skew_student_t_log(real y, real nu, real mu, real sigma, real skew) {
  real lp;
  lp <- log(skew) - log1p(square(skew));
  if (y < mu)
    return lp + student_t_log(y * skew, nu, mu * skew, sigma);
  else
    return lp + student_t_log(y / skew, nu, mu / skew, sigma);
}
\end{verbatim}

@@

%\begin{helvetica}
\smallskip
\begin{scriptsize}
\begin{tabular}{lrrrrrrrr}
\toprule
\input{../analysis/stat-table.tex}
\label{tab:stats}
\end{tabular}
\end{scriptsize}
%\end{helvetica}

@@

%\begin{helvetica}
\singlespacing
\begin{scriptsize}
\begin{longtable}{>{\RaggedRight}m{1.4cm}>{\RaggedRight}p{5.3cm}>{\RaggedRight}p{0.65cm}>{\RaggedRight}p{1.5cm}>{\RaggedRight}p{4.2cm}>{\RaggedRight}p{1.6cm}}
\caption{Populations with a high probability of heavy-tailed dynamics in the base heavy-tailed Gompertz population dynamics model. Shown are the log abundance time series, population descriptions, Global Population Dynamics Database Main IDs, citation for the data source or separate verification literature, a description of the cause of the black-swan events (if known), the probability of heavy tails as calculated by our model, and median estimate of $\nu$ from our model with 90\% quantile credible intervals indicated in parentheses. Red dots on the time series indicate downward black-swan events and blue values indicate upward black-swan events that have a $10^{-4}$ probability or less of occurring if the population dynamics were explained by a Gompertz model with normally distributed process noise with a standard deviation equal to the scale parameter in the fitted $t$ distribution.}\\

>>>>

\begin{verbatim}
real skew_student_t_log(real y, real nu, real mu, real sigma, real skew) {
  real lp;
  lp <- log(skew) - log1p(square(skew));
  if (y < mu)
    return lp + student_t_lpdf(y * skew | nu, mu * skew, sigma);
  else
    return lp + student_t_lpdf(y / skew | nu, mu / skew, sigma);
}
\end{verbatim}

@@

%\begin{helvetica}
\smallskip
\begin{footnotesize}
\begin{tabular}{lrrrrrrrr}
\toprule
\input{../analysis/stat-table.tex}
\label{tab:stats}
\end{tabular}
\end{footnotesize}
%\end{helvetica}

@@

%\begin{helvetica}
\singlespacing
\begin{scriptsize}
\begin{longtable}{>{\RaggedRight}m{1.4cm}>{\RaggedRight}p{5.3cm}>{\RaggedRight}p{0.65cm}>{\RaggedRight}p{1.5cm}>{\RaggedRight}p{4.2cm}>{\RaggedRight}p{1.6cm}}
\caption{Populations with a high ($> 0.6$) probability of heavy-tailed dynamics in the base heavy-tailed Gompertz population dynamics model. Shown are the log abundance time series, population descriptions, Global Population Dynamics Database Main IDs, citation for the data source or separate verification literature, a description of the cause of the black-swan events (if known), the probability of heavy tails as calculated by our model, and median estimate of $\nu$ from our model with 90\% quantile credible intervals indicated in parentheses. Red dots on the time series indicate downward black-swan events and blue values indicate upward black-swan events that have a $10^{-4}$ probability or less of occurring if the population dynamics were explained by a Gompertz model with normally distributed process noise with a standard deviation equal to the scale parameter in the fitted $t$ distribution.}\\
